Concurrent Programming in Harmony

### 2022-01-06 book/paper.tex
Added Towers of Hanoi as an example

<{:const:ref}>

\begin{figure}
\begin{code}
<{:input:../code/clock.hny}>
\end{code}
\caption{\harmonylink{code/clock.hny} Harmony program that finds page replacement anomalies}
\label{fig:clock}
\end{figure}

@@

\index{list module}%
The \texttt{hoare} module implements support for Hoare-style monitors
and condition variables.

>>>>

<{:const:head}>
<{:const:tail}>
\begin{figure}
\begin{code}
<{:input:../code/hanoi.hny}>
\end{code}
\caption{\harmonylink{code/hanoi.hny} Towers of Hanoi}
\label{fig:hanoi}
\end{figure}

As an example of using modules,
\autoref{fig:hanoi} uses (or abuses?) Harmony to solve the
\emph{Towers of Hanoi} problem.
There are three towers with disks of varying sizes.
In the initial configuration, the first tower has three disks (of
sizes 1, 2, and 3), with the largest disk at the bottom, while the
other two towers are empty.  You are allowed to move a top disk
from one tower to another, but you are not allowed to stack a larger
disk on a smaller one.  The objective is to move the disks from the
first tower to the third one.

The program uses the <{list}> module documented in \autoref{ap:list}.
It has methods to extract the \emph{head} (first element) and
the \emph{tail} (remaining elements) of a list.
(The code is simple and available in \texttt{modules/list.hny}.)
The program tries valid moves at random until it finds a solution.
Curiously, the program then asserts <{False}>.  This is to cause
the model checker to stop and output the trace.  If you look in the
output column of the trace, you will find the minimal number of moves
necessary to solve the problem.

<{:const:ref}>
\begin{figure}
\begin{code}
<{:input:../code/clock.hny}>
\end{code}
\caption{\harmonylink{code/clock.hny} Harmony program that finds page replacement anomalies}
\label{fig:clock}
\end{figure}

@@

\index{hoare module}%
The \texttt{hoare} module implements support for Hoare-style monitors
and condition variables.
